---
title: "Improving Model Perfromance / Tuning Parameters"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---


## Tuning Parameter

Generically and regardless of model type, what are the purposes of a model
tuning parameters?

Primarily tuning parameters provides the ability to improve accuracy 
of the prediction of a machine learning model and to reduce the variance of the prediction.  
In addition, there are other tuning paramters to control specific tasks such as : 
  grid search, data-preprocessing, data sampling, data partitioning etc.  
```
```

## Caret Models

This assignment demonstrates the use of caret for constructing models. Each
model should be built and compared using using `Kappa` as the performance
metric calculated using 10-fold repeated cross-validation with 3 folds.

Using the rectangular data that you created for the NYCFlights to create a model
for arr_delay >= 15 minutes.

- glm
- rpart
- knn
- C50
- randomForest
- adaBoost
- Two methods of your choice from the Caret Model List (you will need to install any dependencies)

Save the caret objects with the names provided.

```{r init, warning=FALSE, echo=FALSE, message=FALSE}
library(rpart)
library(caret)
library(dplyr)
library(pROC)
library(partykit)
library(readr)
library(ggplot2)
library(magrittr)
library(data.table)

```{r load data}
# Your Work Here

#loaddata

airports <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/airports.csv") %>% setDT
flights <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/flights.csv") %>% setDT
planes <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/planes.csv") %>% setDT
weather <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/weather.csv") %>% setDT

data_join <- flights %>%
  transform(dephour = floor(dep_time / 100)) %>%
  left_join(.,planes, by=c("tailnum" = "tailnum")) %>% 
  left_join(.,airports,by=c("origin"="faa"))  %>%
  left_join(.,airports,by=c("dest"="faa")) %>%
  left_join(.,weather, by=c("origin"="origin","dephour"="hour","year.x"="year","month"="month","day"="day")) 
head(data_join)
#isolate just the lateflight
data_join$lateflight <- factor(data_join$arr_delay >= 15) 
#data_join$lateflight %>% qplot

#remove NA data
data_join <- na.omit(data_join [,c("lateflight","dep_delay","month","air_time","distance","carrier","lat.y","lon.y","arr_delay")])

#create training data
set.seed(1234)
inTraining <- createDataPartition(data_join$lateflight, p=0.75,list=FALSE)

#Train the model using caret


training <- data_join[inTraining,]
testing <- data_join[-inTraining,]

# Your work here.
train <- trainControl(method = "cv", number = 10, selectionFunction = "best")

fitformula <- lateflight ~ dep_delay + month + air_time + distance + carrier + lat.y + lon.y
#glm
fit.glm <- train(fitformula, data = training, trControl = train, method = "glm", metric="Kappa")
predict.glm <- predict(fit.glm, testing)
confusionMatrix(predict.glm,testing$lateflight)

#knn
fit.knn  <- train(fitformula, data = training, trControl = train, method = "knn",metric="Kappa")
predict.knn <- predict(fit.knn, testing)
confusionMatrix(predict.knn,testing$lateflight)
  
#rpart

fit.rpart  <- train(fitformula, data = training, trControl = train, method = "rpart", metric="Kappa")
predict.rpart <- predict(fit.knm, testing)
cm.rpart(predict.rpart,testing$lateflight)

#rf

fit.rf  <- train(fitformula, data = training, trControl = train, method = "rf", metric="Kappa")
predict.rf <- predict(fit.rf, testing)
confusionMatrix(predict.rf,testing$lateflight)

#C5.0

fit.c50  <- train(fitformula, data = training, trControl = train, method = "C5.0", metric="Kappa")
predict.c50 <- predict(fit.c50, testing)
confusionMatrix(predict.c50,testing$lateflight)

#tuning the model

grid_c50 <- expand.grid(.model = c("rules", "tree"), 
      .trials = c(1,2,5),
      .winnow = "FALSE")

fit.c50 = train(fitformula, data = training, trControl = train, method = "C5.0", 
                metric="Kappa",
                tuneGrid = grid_c50)

predict.c50 <- predict(fit.c50, testing)
confusionMatrix(predict.c50,testing$lateflight)


```

Compare the  models?

The confusion matrix of each model is displayed.  We will use the results of the cm as the 
basis to compare the models.  

Which is best?  Why?

In terms of best accuracy and kappa, the random forest model is best.  It seems to be overfitting.

```
```
